Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>

### 2022-11-18 index.Rmd
mastodon

<div style="text-align: center; align:center"> 
<IMG SRC="round.jpg"> 
<br>
<br>
<br>
Andres Karjus, research fellow, CUDAN lab, Tallinn University<br>
&nbsp;&nbsp;&nbsp;<a href="mailto:andres.karjus --at-- tlu.ee">email</a>  |  <a href="https://twitter.com/AndresKarjus">twitter</a>
<br>
</div>

>>>>

<div style="text-align: center; align:center"> 
<IMG SRC="round.jpg"> 
<br>
<br>
<br>
Andres Karjus, research fellow, CUDAN lab, Tallinn University<br>
&nbsp;&nbsp;&nbsp;<a href="mailto:andres.karjus --at-- tlu.ee">email</a>  |  <a href="https://twitter.com/AndresKarjus">twitter</a> | <a href=https://mastodon.social/@andreskarjus">mastodon</a>
<br>
</div>
